Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2012-05-15 extended_catalog/external_review_reply/replies_to_review_comments.tex

\begin{referee}
Major issues :

The authors use a uniform disk model for fitting the extended sources.
However many sources show a complex morphology (for example, not radial symmetric)
They should quantify how the results they are presenting depend on the actual shape of the sources.
\end{referee}

\begin{reply}
In the new draft, Section 2 has new text defining TS.
Section 3 has been renamed (Validation of the TS Distribution) and has been
divided into three sections. The original section is now section 3.1
(now called Point-like Source Simulations Over a Uniform Background).
I will describe section 3.2 in reply to the next question.

There is also a new section 3.3 (Extended Source Simulations Over a Structured Background). 
In this section, we address your question by performing
a dedicated Monte Carlo study of W44 simulated with a ring-type spatial
model. By fitting the source with different spatial models, we assess
this bias and find it to be very small.

@@

\begin{reply}
Concerning the extension significance test, it actually relies not exactly
on Wilk's theorem (which does not hold for the extension test)
but on Chernoff's theorem (see ``On the Distribution of the Likelihood 
Ratio'', \url{http://www.jstor.org/stable/10.2307/2236839}).
we also extensively validated it
against Monte Carlo simulations. Furthermore, the high energy astrophysics
community has a lot of experience with the likelihood ratio test applied to
nested models. So we are very confident that we can apply it to the actual
data.

Concerning the test comparing two point-like sources to one extended
source, we find the desire for a Bayesian test more compelling since the
models are not nested. We considered the BIC test but found that it would
not work well for LAT data. The reason for this is described in the text.
We alternatively considered the AIC test and
found that it is mathematically equivalent to the test we actually performed,
putting the test on firmer ground. We have
added a new paragraph to Section 5 (Testing Against Source Confusion)
that describes this.
\end{reply}

\begin{referee}
Finally, I can suggest that the lead author discuss the issue with experts
at his institution, as Stanford's Dept. of Statistics is universally
recognized as the best in the nation. They might provide a balanced
judgment whether the BIC is substantially better than the LRT in the
situation under study.
\end{referee}

\begin{reply}
Thanks for the suggestion.  In addition to the above changes, we have
replaced a few references to ``catalog sources'' with ``2FGL sources''
for clarification. We have also fixed a few bibliographical entries. 
\end{reply}

### 2012-05-15 extended_catalog/paper/extended_search.tex
new draft

We performed a second simulation to show that the theoretical distribution
for \tsext is still preserved when the point-like sources are present over
a highly-structured diffuse background.
Our simulation setup was the same as above except that the sources were
simulated on top of and analyzed assuming the presence of the standard
Galactic diffuse and isotropic background models used in 2FGL.  In our
simulations, we selected our sources to have a random position on the sky
such that the absolute value of the galactic latitude of the source was
less than 5\degree. This probes the most structured areas of the 
Galactic background.

To limit the number of tests, we selected only one flux
level for each of the four spectral indices and we performed
this test only in the 1 \gev to 100 \gev energy range. 
The fluxes were selected so that $\ts\sim50$. We do not
expect to be able to spatially resolve sources much dimmer than this
and sources much brighter are less likely to be affected by the 
structured background.

Because the Galactic diffuse emission is highly structure, the point-source
sensitivity can vary significantly across the galactic plane.
To account for this, we scaled the flux (for a given spectral index)
so that the source always has approximately the same signal-to-noise ratio:
\begin{equation}
  \label{scale_flux_by_background}
  F(\vec{x}) = F(\text{GC}) \times \left(
  \frac{B(\vec{x})}{B(\text{GC})}\right)^{1/2}.
\end{equation}
Here, $\vec{x}$ is the position of the simulated source, $F$ is the integral
flux of the source from 100 \mev to 100 \gev, $F(\text{GC})$
is the same quantity if the source was at the galactic center, $B$
is the integral of the Galactic diffuse and isotropic emission
from 1 \gev to 100 \gev at the position of the source, and $B(\text{GC})$ is the same quantity
if the source was at the galactic center.  For the four spectral models,
Table~\ref{ts_ext_num_sims} lists $F(\text{GC})$ and the average value of \ts.

For each spectrum, we performed $\sim90,000$ simulations.
Figure~\ref{tsext_plane_plot} shows the cumulative density
of \tsext for each spectrum. For small values of \tsext,
there is good agreement between the simulations and
theory.  For the highest values of \tsext, there is possibly
a small discrepancy, but limited statistics makes this hard to quantify.
Therefore, we are confident we can used \tsext as a robust measure of
statistical significance when testing LAT-detected sources for extension.

@@

We also performed a Monte Carlo study to show that incorrectly modeling the
spatial extension of an extended source does not substantially bias
the spectral fit of the source, although it does alter the value of the \ts.
To assess this, we simulated the spatially extended ring-type SNR W44.
We selected W44 because it is the most significant extended source detected by the LAT 
that has a non-radially symmetric photon-distribution \citep{w44}.

W44 was simulated with a power-law spectral model with an integral flux
of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100
\gev and a spectral index of 2.66.
The flux and spectral index of this source
was taken from our analysis of W44 which will be described in Section~\ref{validate_known}.

W44 was simulated with the elliptical ring spatial model described in
\cite{w44}. For reference, the ellipse has a semi-major axis of 0\fdg3,
a semi-minor axis of 0\fdg19, a position angle of $147\degree$
measured east of celestial north, and the ring's inner radius is 0.75 times
the outer radius.

We used a simulation setup similar to that described in
Section~\ref{monte_carlo_validation}, but the sources were simulated on
top of and analyzed assuming the presence of the standard Galactic diffuse and
isotropic background model used in 2FGL.  The simulations were
in the 1 \gev to 100 \gev energy range and
W44 was simulated over the two-year time range used in 2FGL. 
In the simulations, we disabled the inherent energy dispersion of photons
by the LAT to isolate the effects due to changing the assumed spatial model. 
The bias caused by ignoring energy dispersion 
will be discussed in an upcoming paper by the LAT collaboration \citep{lat_on_orbit_psf}.
In total, we performed 985 statistically independent simulations.

The simulated sources were fit using a point-like spatial model,
a radially-symmetric uniform Gaussian and disk spatial model, 
an elliptical disk spatial model, and finally with an elliptical
ring spatial model.
We obtained the best fit spatial parameters using \pointlike and, 
with these parameters, obtained the best fit spectral parameters 
using \gtlike.

Figure~\ref{ts_comparison_w44sim}a shows that the simulations of W44
are very significant ($\ts\sim3500$) when fit as point-like sources.
Figure~\ref{ts_comparison_w44sim}b shows that the simulations are
highly extended ($\tsext\sim250$) when fit with any of the extended
spatial models.  On average \tsext is somewhat larger when fitting
the sources with more accurate spatial models.  This shows that
assuming an incorrect spatial model will cause the source's
significance to be underestimated.  Figure~\ref{ts_comparison_w44sim}c
shows that the sources were fit better when assuming an elliptical
disk spatial model compared to a uniform disk spatial model
($\ts_\text{elliptical\ disk}-\ts_\text{disk}\sim30$).  Finally,
Figure~\ref{ts_comparison_w44sim}d shows that the sources were
fit somewhat better assuming an elliptical ring spatial model
compared to an elliptical disk spatial model ($\ts_\text{elliptical\
ring}-\ts_\text{elliptical\ disk}\sim9$). This shows that the LAT has
some additional power to resolve substructure in bright extended sources.

Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b clearly show that
no significant bias is introduced by modeling the source as extended
but with an inaccurate spatial model, while a point-like source modeling
results in a $\sim10\%$ and $\sim5\%$ bias in the fit flux and index,
respectively.  
Furthermore, Figure~\ref{bias_w44sim}c shows that the \rsixeight estimate of
the extension size is very mildly biased ($\sim10\%$) toward higher values
when inaccurate spatial models are used, and thus represent a reasonable
measurement of the true 68\% containment radius for the source.

For completeness, Figure~\ref{bias_w44sim}d and Figure~\ref{bias_w44sim}e 
shows that there are 
no systematic biases in the
distribution of best
fit elliptical eccentricities and orientation angles
when the sources were fit with elliptical
spatial models.  
The eccentricity is defined as
$\sqrt{1-b^2/a^2}$, where $a$ is the length of the semi-major axis and
$b$ is the length of the semi-minor axis.  
Finally, Figure~\ref{bias_w44sim}f shows that the distribution of best fit
inner ring fractions is unbiased when the sources were fit with the elliptical
ring spatial model.
}

@@

\newtext{
We considered using 
the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test} as
an alternative Bayesian formulation for this test, but it is difficult to apply
to LAT data because it contains a term including the number of data points. For LAT data,
this is not a clear concept because there are many pixels included in an analysis that contribute only
 marginally to the analysis of a given source.

@@

Because the two point-like source hypotheses has
three more parameters than the single extended source hypothesis (two spatial
parameters and two spectral parameters compared to one extension parameter),
we note that the $\tsext>\tsinc$ test is mathematically equivalent to testing that
$\aic_\text{ext} < \aic_\text{2pts} - 6$.
Thus our criterion based on the \ts value is equivalent to requesting
that the \aic-based empirical support for the two-point-like-source model be
``considerably less'' than for the extended source model, following the
classification by \cite{aic_stats_book}.
}

@@

Following 2FGL, the LAT Collaboration published the Second LAT AGN
Catalog (2LAC), a list of high latitude ($|b|>10\degree$) sources
that had a high probability association with AGN \citep{second_agn_cat}.
2LAC associated 1016 2FGL sources with AGN.  To avoid systematic problems
with AGN classification, we selected only the 885 AGN which made it into
the clean AGN sub-sample defined in the 2LAC paper.  An AGN association is considered clean only
if it has a high probability of association $P\ge 80\%$, if it is the
only AGN associated with the catalog source, and if 
no analysis flags have been set for the source
in the 2FGL catalog. These last two conditions are important for our
analysis. Source confusion may look like a spatially extended source
and flagged catalog sources may correlate with unmodeled structure in
the diffuse emission.

@@

Ideally, we would apply a completely blind and uniform search that
tests the extension of each catalog source in the presence of all other
2FGL sources to find a complete list of all spatially extended sources.
As our test of AGN in Section~\ref{test_2lac_sources} showed, at high
Galactic latitude where the source density is not as large and the
diffuse emission is less structured, this method works well.

@@

For each candidate that was not biased by neighboring point-like
sources or by large-scale residuals in the diffuse emission model, we
improved the model of the region by deciding on a case by case basis which
background point-like sources should be kept.  We kept in our model the
sources that we
believed represented physically distinct sources and we removed 
sources that we believed were included in the 2FGL catalog to compensate
for residuals induced by not modeling the extension of the source.
Soft nearby point-like 2FGL sources that were not significant at higher energies
were frozen to the spectras predicted by 2FGL.
When deciding
which background sources to keep and which to remove, we used as much as possible
multiwavelength information about possibly extended source counterparts
to help guide our choice. For each extended source presented in 
Section~\ref{new_ext_srcs_section}, we describe any modifications from 2FGL
of the background model that were performed.
\newtext{In Table~\ref{fake_2fgl_sources}, we summarize the sources that were 
included in 2FGL to account for residuals induced by not modeling the extensions of
nearby extended sources.}

@@

2FGL\,J0823.0$-$4246 was found by our search to be an extended source
candidate in the 1 \gev to 100 \gev energy range and is spatially
coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
a counts map of this source. There are two nearby catalog sources 2FGL\,J0823.4$-$4305
and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
do not appear to represent physically distinct sources.
We conclude that
these nearby point-like sources
were included in the 2FGL catalog to compensate for residuals induced
by not modeling the extension of this source and
removed them from our model of the sky.
After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension 
$\sigma=0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with 
$\tsext=48.0$.  Figure~\ref{snr_seds} shows the spectrum of
this source.

@@

2FGL\,J0851.7$-$4635 was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the SNR Vela Jr. This source was recently studied by the LAT
Collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
map of the source.  Overlaid on Figure~\ref{Vela_Jr} are \tev
contours of Vela Jr. \citep{vela_jr_hess}.
There are three
point-like catalog sources 2FGL\,J0848.5$-$4535,
2FGL\,J0853.5$-$4711, and
2FGL\,J0855.4$-$4625
which correlate with the 
multiwavelength
emission of
this SNR but do not appear to be physically distinct sources.
They were most likely included in the 2FGL catalog to compensate for residuals
induced by not modeling the extension of Vela Jr. and were removed
from our model of the sky.

With this model of the background, 2FGL\,J0851.7$-$4635 was found to
have an extension of $\sigma=1\fdg15\pm0\fdg08_\stat\pm0\fdg02_\sys$ with
$\tsext=86.8$.  The LAT size matches
well the \tev morphology of Vela Jr.  While fitting the extension
of 2FGL\,J0851.7$-$4635, we iteratively relocalized the positions
of the nearby point-like catalog source 2FGL\,J0854.7$-$4501 to
$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies.

@@

2FGL\,J1615.2$-$5138 was found
 to have an extension $\sigma=0\fdg42\pm0\fdg04_\stat\pm0.02_\sys$
with $\tsext=46.5$.
To test for the possibility that
2FGL\,J1615.2$-$5138 is not spatially extended but instead composed
of two point-like sources (one of them represented in the 2FGL catalog by
2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
sources.  \newtext{Because $\tsinc=35.1$ is less than $\tsext=46.5$, we conclude that
this emission does not originate from two nearby point-like sources.}

@@

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/ts_comparison_w44sim_color.eps}
    \else
    \plotone{mc_plots/ts_comparison_w44sim_bw.eps}
    \fi
    % this plot came from $w44simplots/plot_ts_values.py
    \caption{
    \newtext{The distribution of \ts values when fitting statistically
    independent simulations of W44. (a) is the distribution of \ts values
    when fitting W44 as a point-like source and (b) is the
    distribution of \tsext when fitting the source with a uniform disk and Gaussian
    spatial model. (c) is the distribution of the change in TS when
    fitting the source with an elliptical disk spatial model compared to
    fitting it with a radially-symmetric disk spatial model and (d) 
    when fitting the source with an elliptical ring spatial model compared
    to an elliptical disk spatial model.
    }
    }\label{ts_comparison_w44sim}
\end{figure}

@@

\tablecomments{
\newtext{
For each new extended source, we list nearby catalog
sources that were included in 2FGL to account for residuals induced
by not modeling the extension of the extended source.
}
}
\end{deluxetable}

>>>>

We performed a second set of simulation to show that the theoretical distribution
for \tsext is still preserved when the point-like sources are present over
a highly-structured diffuse background.
Our simulation setup was the same as above except that the sources were
simulated on top of and analyzed assuming the presence of the standard
Galactic diffuse and isotropic background models used in 2FGL.  In our
simulations, we selected our sources to have random positions on the sky
such that they were within 5\degree of the Galactic plane. This probes the 
brightest and most strongly contrasting areas of the Galactic background.

To limit the number of tests, we selected only one flux
level for each of the four spectral indices and we performed
this test only in the 1 \gev to 100 \gev energy range. 
As described below, The fluxes were selected so that $\ts\sim50$. We do not
expect to be able to spatially resolve sources much dimmer than this
and the results for sources much brighter are less likely to be affected by the 
structured background.

Because the Galactic diffuse emission is highly structure with
strong gradients, the point-source
sensitivity can vary significantly across the Galactic plane.
To account for this, we scaled the flux (for a given spectral index)
so that the source always has approximately the same signal-to-noise ratio:
\begin{equation}
  \label{scale_flux_by_background}
  F(\vec{x}) = F(\text{GC}) \times \left(
  \frac{B(\vec{x})}{B(\text{GC})}\right)^{1/2}.
\end{equation}
Here, $\vec{x}$ is the position of the simulated source, $F$ is the integral
flux of the source from 100 \mev to 100 \gev, $F(\text{GC})$
is the same quantity if the source was at the Galactic center, $B$
is the integral of the Galactic diffuse and isotropic emission
from 1 \gev to 100 \gev at the position of the source, and $B(\text{GC})$ is the same quantity
if the source was at the Galactic center.  For the four spectral models,
Table~\ref{ts_ext_num_sims} lists $F(\text{GC})$ and the average value of \ts.

For each spectrum, we performed $\sim90,000$ simulations.
Figure~\ref{tsext_plane_plot} shows the cumulative density
of \tsext for each spectrum. For small values of \tsext,
there is good agreement between the simulations and
theory.  For the highest values of \tsext, there is possibly
a small discrepancy, but the discrepancy is not statistically significant.
Therefore, we are confident we can use \tsext as a robust measure of
statistical significance when testing LAT-detected sources for extension.

@@

We also performed a Monte Carlo study that (a) shows that we obtain
an unbiased fit of an extended source with a complicated spatial shape so long as
the source is correctly modeled and (b) quantifies the biases 
introduced by incorrectly modeling its spatial structure.
To assess this, we simulated the spatially extended ring-type SNR W44.
We selected W44 because it is the most significant extended source detected by the LAT 
that has a non-radially symmetric photon distribution \citep{w44}.

W44 was simulated with a power-law spectral model with an integral flux
of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100
\gev and a spectral index of 2.66 (see Section~\ref{validate_known}).

W44 was simulated with the elliptical ring spatial model described in
\cite{w44}. For reference, the ellipse has a semi-major axis of 0\fdg3,
a semi-minor axis of 0\fdg19, a position angle of $147\degree$
measured East of celestial North, and the ring's inner radius is 75\% of
the outer radius.

We used a simulation setup similar to that described in
Section~\ref{monte_carlo_validation}, but the sources were simulated on
top of and analyzed assuming the presence of the standard Galactic diffuse and
isotropic background model used in 2FGL.  
We simulated the gamma-ray emission in the 1 \gev to 100 \gev
energy range for the 2-year interval of the 2FGL catalog.
In the simulations, 
we did not include the finite energy resolution of the LAT
to isolate any effects due to changing the assumed spatial model. 
The fitting code we use also ignores this energy dispersion and the
potential bias introduced by this will be discussed in an upcoming paper
by the LAT collaboration \citep{lat_on_orbit_psf}.
In total, we performed 985 independent simulations.

The simulated sources were fit using a point-like spatial model,
a radially-symmetric Gaussian spatial model, a uniform disk spatial model, 
an elliptical disk spatial model, and finally with an elliptical
ring spatial model.
We obtained the best fit spatial parameters using \pointlike and, 
with these parameters, obtained the best fit spectral parameters 
using \gtlike.

Figure~\ref{ts_comparison_w44sim}a 
shows that
the significance of W44 in the simulations is very great ($\ts\sim3500$) 
for a model with a point-like source hypothesis.
Figure~\ref{ts_comparison_w44sim}b shows that 
the significance of the spatial extension is also very great
($\tsext\sim250$).  
On average \tsext is somewhat larger when fitting
the sources with more accurate spatial models.  This shows that
assuming an incorrect spatial model will cause the source's
significance to be underestimated.  Figure~\ref{ts_comparison_w44sim}c
shows that the sources were fit better when assuming an elliptical
disk spatial model compared to a uniform disk spatial model
($\ts_\text{elliptical\ disk}-\ts_\text{disk}\sim30$).  Finally,
Figure~\ref{ts_comparison_w44sim}d shows that the sources were
fit somewhat better assuming an elliptical ring spatial model
compared to an elliptical disk spatial model ($\ts_\text{elliptical\
ring}-\ts_\text{elliptical\ disk}\sim9$). This shows that the LAT has
some additional power to resolve substructure in bright extended sources.

Figure~\ref{bias_w44sim} shows that there are no systematic biases in the
distribution of best fit (a) flux (b) spectral index (c) \rsixeight
(d) elliptical eccentricity (e) elliptical orientation angle and (f) inner
ring fraction when the simulated extended sources were fit with the
elliptical ring spatial model. For the elliptical spatial models, \rsixeight
is computed by numeric integration.
Figures~\ref{bias_w44sim}a and~\ref{bias_w44sim}b show that
no significant bias is introduced by modeling the source with the 
other extended spatial models, while modeling the source as point-like
results in $\sim10\%$ and $\sim5\%$ biases in the fit flux and index,
respectively.  
Furthermore, Figure~\ref{bias_w44sim}c shows that the \rsixeight estimate of
the extension is very mildly biased ($\sim10\%$) toward higher values
when inaccurate spatial models are used, and thus \rsixeight for any of
these spatial models can be used as a reasonable measurement of the true
68\% containment radius for the source.
}

@@

\newtext{
We considered using 
the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test} as
an alternative Bayesian formulation for this test, but it is difficult to apply
to LAT data because it contains a term including the number of data points. 
For studying gamma-ray sources in LAT data, we analyze relatively large
regions of the sky to better define the contributions from diffuse
backgrounds and nearby point sources. This is important for accurately
evaluating source locations and fluxes but the fraction of data directly
relevant to the evaluation of the parameters for the source of interest
is relatively small.

@@

Because the two point-like source hypothesis has
three more parameters than the single extended source hypothesis (two spatial
parameters and two spectral parameters compared to one extension parameter),
we note that the $\tsext>\tsinc$ test is mathematically equivalent to testing that
$\aic_\text{ext} < \aic_\text{2pts} - 6$.
Thus our criterion based on the \ts value is equivalent to requesting
that the \aic-based empirical support for the two-point-like-source model be
``considerably less'' than for the extended source model, following the
classification by \cite{aic_stats_book}.
}

@@

Following 2FGL, the LAT Collaboration published the Second LAT AGN
Catalog (2LAC), a list of high latitude ($|b|>10\degree$) sources
that had a high probability association with AGN \citep{second_agn_cat}.
2LAC associated 1016 2FGL sources with AGN.  To avoid systematic problems
with AGN classification, we selected only the 885 AGN which made it into
the clean AGN sub-sample defined in the 2LAC paper.  An AGN association is considered clean only
if it has a high probability of association $P\ge 80\%$, if it is the
only AGN associated with the 2FGL source, and if 
no analysis flags have been set for the source
in the 2FGL catalog. These last two conditions are important for our
analysis. Source confusion may look like a spatially extended source
and flagged 2FGL sources may correlate with unmodeled structure in
the diffuse emission.

@@

Ideally, we would apply a completely blind and uniform search that
tests the extension of each 2FGL source in the presence of all other
2FGL sources to find a complete list of all spatially extended sources.
As our test of AGN in Section~\ref{test_2lac_sources} showed, at high
Galactic latitude where the source density is not as large and the
diffuse emission is less structured, this method works well.

@@

For each candidate that was not biased by neighboring point-like
sources or by large-scale residuals in the diffuse emission model, we
improved the model of the region by deciding on a case by case basis which
background point-like sources should be kept.  We kept in our model the
sources that we
believed represented physically distinct sources and we removed 
sources that we believed were included in the 2FGL catalog to compensate
for residuals induced by not modeling the extension of the source.
Soft nearby point-like 2FGL sources that were not significant at higher energies
were frozen to the spectras predicted by 2FGL.
When deciding
which background sources to keep and which to remove, we used as much as possible
multiwavelength information about possibly extended source counterparts
to help guide our choice. For each extended source presented in 
Section~\ref{new_ext_srcs_section}, we describe any modifications from 2FGL
of the background model that were performed.
\newtext{In Table~\ref{fake_2fgl_sources}, we summarize the sources in
the 2FGL catalog that we have concluded here correspond to residuals
induced by not modeling the extensions of nearby extended sources.}

@@

2FGL\,J0823.0$-$4246 was found by our search to be an extended source
candidate in the 1 \gev to 100 \gev energy range and is spatially
coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
a counts map of this source. There are two nearby 2FGL sources 2FGL\,J0823.4$-$4305
and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
do not appear to represent physically distinct sources.
We conclude that
these nearby point-like sources
were included in the 2FGL catalog to compensate for residuals induced
by not modeling the extension of this source and
removed them from our model of the sky.
After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension 
$\sigma=0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with 
$\tsext=48.0$.  Figure~\ref{snr_seds} shows the spectrum of
this source.

@@

2FGL\,J0851.7$-$4635 was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the SNR Vela Jr. This source was recently studied by the LAT
Collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
map of the source.  Overlaid on Figure~\ref{Vela_Jr} are \tev
contours of Vela Jr. \citep{vela_jr_hess}.
There are three
point-like 2FGL sources 2FGL\,J0848.5$-$4535,
2FGL\,J0853.5$-$4711, and
2FGL\,J0855.4$-$4625
which correlate with the 
multiwavelength
emission of
this SNR but do not appear to be physically distinct sources.
They were most likely included in the 2FGL catalog to compensate for residuals
induced by not modeling the extension of Vela Jr. and were removed
from our model of the sky.

With this model of the background, 2FGL\,J0851.7$-$4635 was found to
have an extension of $\sigma=1\fdg15\pm0\fdg08_\stat\pm0\fdg02_\sys$ with
$\tsext=86.8$.  The LAT size matches
well the \tev morphology of Vela Jr.  While fitting the extension
of 2FGL\,J0851.7$-$4635, we iteratively relocalized the positions
of the nearby point-like 2FGL source 2FGL\,J0854.7$-$4501 to
$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies.

@@

2FGL\,J1615.2$-$5138 was found
 to have an extension $\sigma=0\fdg42\pm0\fdg04_\stat\pm0.02_\sys$
with $\tsext=46.5$.
To test for the possibility that
2FGL\,J1615.2$-$5138 is not spatially extended but instead composed
of two point-like sources (one of them represented in the 2FGL catalog by
2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
sources.  \newtext{Because $\tsinc=35.1$ is less than $\tsext=46.5$, we conclude that
this emission does not originate from two closely-spaced point-like sources.}

@@

\clearpage
\begin{figure}
    \ifcolorfigure
    \plotone{mc_plots/ts_comparison_w44sim_color.eps}
    \else
    \plotone{mc_plots/ts_comparison_w44sim_bw.eps}
    \fi
    % this plot came from $w44simplots/plot_ts_values.py
    \caption{
    \newtext{The distribution of \ts values when fitting statistically
    independent simulations of W44. (a) is the distribution of \ts values
    when fitting W44 as a point-like source and (b) is the
    distribution of \tsext when fitting the source with a uniform disk or a 
    radially-symmetric Gaussian
    spatial model. (c) is the distribution of the change in TS when
    fitting the source with an elliptical disk spatial model compared to
    fitting it with a radially-symmetric disk spatial model and (d) 
    when fitting the source with an elliptical ring spatial model compared
    to an elliptical disk spatial model.
    }
    }\label{ts_comparison_w44sim}
\end{figure}

@@

\tablecomments{
\newtext{For each new extended source, we list nearby 2FGL
soruces that we have concluded here correspond to residuals induced by not
modeling the extensions of nearby extended sources.}
}
\end{deluxetable}
